---
title: "Does International Shipping Affect Product Ratings ?"
output: html_document
date: "2025-01-25"
---
```{r setup, include=FALSE}


library(tidyverse)
library(modelr)
library(tidybayes)
library(dplyr)
library(bayesplot)
library(posterior)
library(ggplot2)
library(patchwork)
library(brms)
library(ROCR)


```



#Load Dataset

```{r}

merch_data <- read.csv("merch_sales.csv")
#install.packages("data.table")
head(merch_data)


```


```{r}

names(merch_data)

```


################### DATA UNDERSTANDING and DATA PRE-PROCESSING  ######################
######################################################################################
######################################################################################


```{r}
# Selecting Relevant Columns

merch_data_new <- merch_data[, !names(merch_data) %in% c("Order.ID", "Order.Date", "Order.Location", "Review")]

# View of Updated Dataset

head(merch_data_new)

```


```{r}
names(merch_data_new)
```

```{r}

# Encoding non-numerical columns as factors
merch_data_new$Buyer.Gender <- as.numeric(as.factor(merch_data_new$Buyer.Gender))
merch_data_new$International.Shipping <- as.numeric(as.factor(merch_data_new$International.Shipping))
merch_data_new$Rating <- as.numeric(as.factor(merch_data_new$Rating))
merch_data_new$Product.ID <- as.numeric(as.factor(merch_data_new$Product.ID))
merch_data_new$Product.Category <- as.numeric(as.factor(merch_data_new$Product.Category))
head(merch_data_new)


```

```{r}
# Computing the correlation matrix for the numeric data

cor_matrix <- cor(merch_data_new, use = "complete.obs")


# Visualizing the correlation matrix

library(corrplot)

# Save the plot
png("correlation_matrix.png", width = 1200, height = 1200, res = 150)

# Plot the correlation matrix 
corrplot(cor_matrix,
         method = "color",        
         type = "upper",          # display upper triangular matrix
         tl.col = "black",        
         tl.cex = 1.5,            
         number.cex = 1.2,       
         addCoef.col = "black",  
         mar = c(0, 0, 2, 0))     


dev.off()

```


```{r}

# Converting the numeric Rating column to an ordered factor

merch_data_new$Rating <- factor(merch_data_new$Rating, 
                      levels = c(1, 2, 3, 4, 5),          # Specifying the order explicitly
                      ordered = TRUE)

# Verifying the conversion

str(merch_data_new$Rating)

head(merch_data_new$Rating)

```


```{r}

write.csv(merch_data_new, "merch_sales_new_factor.csv", row.names = FALSE)

```



```{r}

merch_data_updated <- read.csv("merch_sales_new_factor.csv")
head(merch_data_updated)

```


```{r}

# Distribution Of Rating Column

# png("Distribution Of Ratings.png", width = 2000, height = 1500, res = 300)

# Creating a bar plot for the ordinal Rating column

barplot(table(merch_data_updated$Rating),
        main = "Distribution of Ratings",
        xlab = "Ratings",
        ylab = "Frequency",
        col = "lightblue",
        border = "black")



```


```{r}

# Plot for "Rating vs International Shipping"

# png("Rating vs International Shipping.png", width = 2000, height = 1500, res = 300)

boxplot(as.numeric(merch_data_updated$Rating) ~ merch_data_updated$International.Shipping,
        main = "Rating vs International Shipping",
        xlab = "International Shipping",
        ylab = "Rating",
        col = c("skyblue", "orange"),
        names = c("Domestic", "International"),
        border = "black")


```

```{r} 

# Recoding (Numeric) Rating column back to ordered factor
merch_data_updated$Rating <- factor(merch_data_updated$Rating, 
                      levels = c(1, 2, 3, 4, 5), 
                      ordered = TRUE)


str(merch_data_updated$Rating)


head(merch_data_updated$Rating)

```



```{r}

# Factoring Product.Category

merch_data_updated$Product.Category <- as.factor(merch_data_updated$Product.Category)
levels(merch_data_updated$Product.Category)

```


```{r}

# Re-encoding  International.Shipping back to a factor
merch_data_updated$International.Shipping <- factor(
  merch_data_updated$International.Shipping,
  levels = c(1, 2),  
  labels = c("Yes", "No")  # referencing
)

```


```{r}

# Factoring Buyer.Gender
merch_data_updated$Buyer.Gender <- factor(merch_data_updated$Buyer.Gender, 
                                      levels = c(1, 2), 
                                      labels = c("Female", "Male"))  # referencing

```


```{r}
levels(merch_data_updated$Buyer.Gender)

head(merch_data_updated)

```


```{r}

# Recoding  Product.ID back to a factor

merch_data_updated$Product.ID <- as.character(merch_data_updated$Product.ID)
merch_data_updated$Product.ID <- as.factor(merch_data_updated$Product.ID)


```


```{r}
head(merch_data_updated)
```



############## MODEL IMPLEMENTATION #####################
#########################################################
#########################################################


# ORDINAL MODEL WITH ALL FEATURE (Model 1)


<!-- ```{r} -->

<!--      prior <- c( -->
<!--      set_prior("normal(0, 5)", class = "b"),           # Prior for regression coefficients -->
<!--      set_prior("normal(0, 5)", class = "Intercept")    # Prior for thresholds -->
<!--   ) -->

<!--     # Fit the Bayesian ordinal regression model -->
<!--     ordinal_model_fit1 <- brm( -->
<!--     Rating ~ `International.Shipping` +  `Buyer.Age` + -->
<!--               `Sales.Price` + `Quantity`, -->
<!--     data = merch_data_updated, -->
<!--     family = cumulative(),   # cumulative logit  -->
<!--     prior = prior, -->
<!--     chains = 4,              # Number of MCMC chains -->
<!--     iter = 2000,             # Number of iterations per chain -->
<!--     cores = parallel::detectCores() # Use all available cores -->
<!--  ) -->

<!-- ``` -->


<!-- ```{r} -->
<!--  saveRDS(ordinal_model_fit1, file = "ordinal_model_fit1.rds") -->

<!-- ``` -->



```{r}
ordinal_model_fit1 <- readRDS("ordinal_model_fit1.rds")
```


```{r}
summary(ordinal_model_fit1)
```


```{r}
plot(ordinal_model_fit1, type = "dens overlay")

```


```{r}

# Open a PNG graphics device
#png("MCMC_ordinal_model_fit1.png", width = 2000, height = 1500, res = 300)
mcmc_trace(ordinal_model_fit1)
#dev.off()

#png("MCMC_dens_ordinal_model_fit1.png", width = 2000, height = 1500, res = 300)
mcmc_plot(ordinal_model_fit1 , type = "dens")
#dev.off()

```



```{r}

# Posterior predictive checks
#png("pp_check_density_ordinal_model_fit1.png", width = 2000, height = 1500, res = 300)
pp_check(ordinal_model_fit1, ndraws = 100)
#dev.off()

# Posterior predictive check
#png("pp_check_bar_ordinal_model_fit1.png", width = 2000, height = 1500, res = 300)
pp_check(ordinal_model_fit1, type = "bars")
#dev.off()

```



```{r}

# Plotting conditional effects for International Shipping
#png("conditional_effects_plot_ordinal_model_fit1.png", width = 2000, height = 1500, res = 300)
conditional_effects_plot <- conditional_effects(
  ordinal_model_fit1,
  effects = "International.Shipping",
  categorical = TRUE
)
plot(conditional_effects_plot)

```



```{r}
#  LOO on Ordinal_Model1
loo_ordinal_fit1 <- loo(ordinal_model_fit1)

print(loo_ordinal_fit1)  # View the LOO results

#png("loo_ordinal_model_fit1.png", width = 2000, height = 1500, res = 300)
plot(loo_ordinal_fit1)   # Plot the LOO results


```



# ORDINAL MODEL WITH INTERACTION : INTERNATIONAL SHIPPING * PRODUCT CATEGORY (Model 2)



<!-- ```{r} -->
<!--   ordinal_model_fit2 <- brm( -->
<!--         formula = Rating ~ International.Shipping * Product.Category,  # Including interaction term -->
<!--         data = merch_data_updated, -->
<!--         family = cumulative(),   -->
<!--         prior = c( -->
<!--         prior(normal(0, 5), class = "b") + -->
<!--         prior("normal(0, 5)", class = "Intercept") #  prior for thresholds and regression coefficients -->
<!--          ), -->
<!--         iter = 2000, -->
<!--         warmup = 1000, -->
<!--         chains = 4, -->
<!--         cores = 4, -->
<!--         seed = 123 -->
<!--         ) -->


<!-- ``` -->


<!-- ```{r} -->

<!-- saveRDS(ordinal_model_fit2, file = "ordinal_model_fit2.rds") -->

<!-- ``` -->



```{r}

ordinal_model_fit2 <- readRDS("ordinal_model_fit2.rds")

```


```{r}
summary(ordinal_model_fit2)

```


```{r}
plot(ordinal_model_fit2)

```


```{r}

#posterior predictive check density

#png("pp_check_density_ordinal_model_fit2.png", width = 2000, height = 1500, res = 300)
pp_check(ordinal_model_fit2, ndraws = 100)
#dev.off()

#posterior predictive check bar plot

#png("pp_check_bar_ordinal_model_fit2.png", width = 2000, height = 1500, res = 300)
pp_check(ordinal_model_fit2 , type = "bars")
#dev.off()

```


```{r}

#png("MCMC_trace_ordinal_model_fit2.png", width = 2000, height = 1500, res = 300)
mcmc_plot(ordinal_model_fit2 , type = "trace")
#dev.off()

#png("MCMC_dens_ordinal_model_fit2.png", width = 2000, height = 1500, res = 300)
mcmc_plot(ordinal_model_fit2 , type = "dens")
#dev.off()

```




```{r}
#png("conditional_effects_plot_ordinal_model_fit2.png", width = 2000, height = 1500, res = 300)

# Conditional effects plot for International Shipping across Product Categories
conditional_effects_plot_interaction <- conditional_effects(
  ordinal_model_fit2, 
  effects = "International.Shipping:Product.Category",
  conditions = data.frame(Product.Category = unique(merch_data_updated$Product.Category))  # Setting conditions
)


plot(conditional_effects_plot_interaction)

```



```{r}

#  LOO on ordinal_model_fit2

loo_ordinal_fit2 <- loo(ordinal_model_fit2)

print(loo_ordinal_fit2)


#png("loo_ordinal_model_fit2.png", width = 2000, height = 1500, res = 300)
plot(loo_ordinal_fit2)


```




<!-- ## Ordinal Model with interaction + additional term -->


<!-- ```{r} -->

<!--  ordinal_model_fit3 <- brm( -->
<!--    formula = Rating ~  International.Shipping + Product.Category * Shipping.Charges,  # Include interaction term + additional term -->
<!--    data = merch_data_updated, -->
<!--    family = cumulative(),  # Ordinal regression -->
<!--    prior = c( -->
<!--      prior(normal(0, 5), class = "b") + -->
<!--      prior("normal(0, 5)", class = "Intercept")# Regularization prior for coefficients -->
<!--    ), -->
<!--    iter = 2000, -->
<!--    warmup = 1000, -->
<!--    chains = 4, -->
<!--    cores = 4, -->
<!--    seed = 123 -->
<!--  )  -->

<!-- ``` -->

<!-- ```{r} -->

<!-- saveRDS(ordinal_model_fit3, file = "ordinal_model_fit3.rds") -->

<!-- ``` -->




<!-- ```{r} -->
<!-- summary(ordinal_model_fit3) -->

<!-- ``` -->



<!-- ```{r} -->
<!-- mcmc_plot(ordinal_model_fit3, type = "trace") -->
<!-- mcmc_plot(ordinal_model_fit3, type = "dens") -->

<!-- ``` -->




<!-- ```{r} -->
<!-- pp_check(ordinal_model_fit3, ndraws = 100) -->
<!-- pp_check(ordinal_model_fit3, type = "bars") -->

<!-- ``` -->



<!-- ```{r} -->
<!-- #  LOO on Ordinal_with_interaction + additional term -->

<!-- loo_ordinal_fit3 <- loo(ordinal_model_fit3) -->
<!-- print(loo_ordinal_fit3)# View the LOO results -->
<!-- plot(loo_ordinal_fit3)# Plot the LOO results -->
<!-- ``` -->







<!-- # Ordinal Model with all features including Shipping.Charges -->

<!-- ```{r} -->

<!--      prior <- c( -->
<!--      set_prior("normal(0, 5)", class = "b"),           # Prior for regression coefficients -->
<!--      set_prior("normal(0, 5)", class = "Intercept")    # Prior for thresholds -->
<!--   ) -->

<!--     # Fit the Bayesian ordinal regression model -->
<!--     ordinal_model_fit4 <- brm( -->
<!--     Rating ~ `International.Shipping` +  `Buyer.Age` + -->
<!--               `Sales.Price` + `Quantity`+ `Shipping.Charges`, -->
<!--     data = merch_data_updated, -->
<!--     family = cumulative(),   # Use the cumulative ordinal family -->
<!--     prior = prior, -->
<!--     chains = 4,              # Number of MCMC chains -->
<!--     iter = 2000,             # Number of iterations per chain -->
<!--     cores = parallel::detectCores() ,# Use all available cores -->
<!--     control = list(adapt_delta = 0.999, max_treedepth = 20) -->
<!--  ) -->

<!-- ``` -->


<!-- ```{r} -->
<!--  saveRDS(ordinal_model_fit4, file = "ordinal_model_fit4.rds") -->

<!-- ``` -->



<!-- ```{r} -->

<!-- ordinal_model_fit4 <- readRDS("ordinal_model_fit4.rds") -->

<!-- ``` -->



<!-- ```{r} -->

<!-- summary(ordinal_model_fit4) -->

<!-- ``` -->





<!-- ```{r} -->
<!-- mcmc_plot(ordinal_model_fit4, type = "trace") -->
<!-- mcmc_plot(ordinal_model_fit4, type = "dens") -->

<!-- ``` -->




<!-- ```{r} -->
<!-- pp_check(ordinal_model_fit4, ndraws = 100) -->
<!-- pp_check(ordinal_model_fit4, type = "bars") -->

<!-- ``` -->



# Bayesian Hierarchical Model with Random effects  (1  | Product.Category/Product.ID) (Model 3)



```{r}

# Checking Nested Structure

# Counting unique Product.Category values for each Product.ID

category_counts <- merch_data_updated %>%
  group_by(Product.ID) %>%
  summarise(unique_categories = n_distinct(Product.Category))

# Finding Product.IDs that appear in more than one category
non_nested_ids <- category_counts %>% filter(unique_categories > 1)


print(non_nested_ids)

```




<!-- ```{r} -->
<!--  prior <- c( -->
<!--     set_prior("normal(0, 5)", class = "b"),               # prior for regression coefficients -->
<!--     set_prior("normal(0, 5)", class = "Intercept"),       # prior for intercepts -->
<!--     set_prior("student_t(3, 0, 2)", class = "sd")         # prior for group-level standard deviations -->
<!--   ) -->


<!--   hierarchical_model <- brm( -->
<!--     Rating ~ International.Shipping + Buyer.Age + -->
<!--            (1  | Product.Category/Product.ID),  # Random effects -->
<!--     data = merch_data_updated , -->
<!--     family = cumulative(), -->
<!--     prior = prior, -->
<!--     chains = 4, -->
<!--     iter = 2000, -->
<!--     control = list(adapt_delta = 0.999, max_treedepth = 20), # for sampling efficiency and convergence issue -->
<!--     cores = parallel::detectCores() -->
<!--   ) -->

<!-- ``` -->



<!-- ```{r} -->
<!-- saveRDS(hierarchical_model, file = "hierarchical_model_new_1.rds") -->

<!-- ``` -->



```{r}
hierarchical_model <- readRDS("hierarchical_model_new_1.rds")

```




```{r}

summary(hierarchical_model)

```



```{r}

#png("MCMC_trace_hierarchical_model.png", width = 2000, height = 1500, res = 300)
mcmc_plot(hierarchical_model, type = "trace")
#dev.off()



#png("MCMC_dens_hierarchical_model.png", width = 2000, height = 1500, res = 300)
mcmc_plot(hierarchical_model, type = "dens")
#dev.off()

```



```{r}

#png("pp_check_density_hierarchical_model.png", width = 2000, height = 1500, res = 300)
pp_check(hierarchical_model, ndraws = 100)
#dev.off()

#png("pp_check_bar_hierarchical_model.png", width = 2000, height = 1500, res = 300)
pp_check(hierarchical_model, type = "bars")
#dev.off()

```




```{r}

# Defining the levels of factors explicitly
conditions <- data.frame(
  Product.Category = levels(merch_data_updated$Product.Category)
)

# Generating conditional effects for "International.Shipping" 

ce <- conditional_effects(
  hierarchical_model,
  effects = "International.Shipping",
  conditions = conditions,
  categorical = TRUE  
)


plot(ce, points = TRUE)

```



```{r}

#png("conditional_effects_plot_hierarchical_model.png", width = 2000, height = 1500, res = 300)

# Conditional effects plot for International Shipping
conditional_effects <- conditional_effects(
  hierarchical_model, 
  effects = "International.Shipping",
  categorical = TRUE
)

# Plot
plot(conditional_effects)


```



```{r}

# Extracting random effects for Product.Category and Product.ID

random_effects <- ranef(hierarchical_model)
print(random_effects)  # Displays the random effect estimates


```

## Random Effects Visualization for Product.Category

```{r}

# Extracting random effects for Product.Category and converting to dataframe

random_effects_df <- as.data.frame(ranef(hierarchical_model)$Product.Category[,, "Intercept"])

# Renaming row names as Category IDs
random_effects_df$Category_ID <- rownames(random_effects_df)

# Checking structure to confirm column names

str(random_effects_df)

```




```{r}

#png("random1.png", width = 2000, height = 1500, res = 300)

# Creating plots for random effects

ggplot(random_effects_df, aes(x = as.factor(Category_ID), y = Estimate)) +
  geom_point(size = 3) + 
  geom_errorbar(aes(ymin = Q2.5, ymax = Q97.5), width = 0.2) +  # Error bars
  geom_hline(yintercept = 0, color = "red") +  # Baseline reference
  labs(title = "Random Effects for Product Categories",
       x = "Product Category",
       y = "Random Intercept Estimate") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 12))  


```



<!-- Each point represents the estimated random intercept for a Product.Category. -->
<!-- The vertical error bars represent uncertainty -->
<!-- If the error bars overlap 0, suggest category-level differences are not strongly significant. -->
<!-- Product.Category significantly affects ratings if categories had shown large variations. -->


## Random Effects Visualization for Product.ID


```{r}

# Extracting random effects & converting to dataframe
random_effects_id <- as.data.frame(ranef(hierarchical_model)$Product.ID[, , "Intercept"])

# Converting row names to column
random_effects_id <- tibble::rownames_to_column(random_effects_id, var = "Product_ID")
str(random_effects_df)

```


```{r}
str(ranef(hierarchical_model)$Product.ID)

```


```{r}

# Re-extracting Product.Id as it is nested under Product.Category

random_effects_id <- as.data.frame(ranef(hierarchical_model)$'Product.Category:Product.ID'[, , "Intercept"])
random_effects_id <- tibble::rownames_to_column(random_effects_id, var = "Product_ID")

str(random_effects_id)  # Checking if data exists

```


```{r}

# Factoring character(chr) for proper Visualization

random_effects_id$Product_ID <- as.factor(random_effects_id$Product_ID)

```


```{r}
# Plot Random Effects Product.ID

#png("random2.png", width = 2000, height = 1500, res = 300)

ggplot(random_effects_id, aes(x = Product_ID, y = Estimate)) +
  geom_point(size = 3) +  # Dots represent intercept estimates
  geom_errorbar(aes(ymin = Q2.5, ymax = Q97.5), width = 0.2) +  # Error bars indicating uncertainty
  geom_hline(yintercept = 0, color = "purple") +  
  labs(title = "Random Effects for Product IDs",
       x = "Product ID",
       y = "Random Intercept Estimate") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 10)) 

```




```{r}

#  LOO on Hierarchical Model

loo_hierarchical_model <- loo(hierarchical_model)
print(loo_hierarchical_model)# View the LOO results

#png("loo_hierarchical_model.png", width = 2000, height = 1500, res = 300)
plot(loo_hierarchical_model)

```







## Bayesian Hierarchical Model with Random Effects Product.Category/Product.Id and Buyer.Gender



<!-- ```{r} -->

<!-- hierarchical_model_2 <- brm( -->
<!--   Rating ~ International.Shipping + -->
<!--     (1 + International.Shipping| Product.Category/Product.ID) + (1 | Buyer.Gender), -->
<!--   data = merch_data_updated, -->
<!--   family = cumulative(), -->
<!--   prior = c( -->
<!--     set_prior("normal(0, 5)", class = "b"), -->
<!--     set_prior("normal(0, 5)", class = "Intercept"), -->
<!--     set_prior("student_t(3, 0, 2)", class = "sd") -->
<!--   ), -->
<!--   chains = 4, -->
<!--   iter = 2000, -->
<!--   control = list(adapt_delta = 0.999, max_treedepth = 20), -->
<!--   cores = parallel::detectCores() -->
<!-- ) -->

<!-- ``` -->



<!-- ```{r} -->
<!--  saveRDS(hierarchical_model_2, file = "hierarchical_model_new_2.rds") -->
<!-- ``` -->


```{r}
hierarchical_model_2 <- readRDS("hierarchical_model_new_2.rds")
```



```{r}
summary(hierarchical_model_2)
```



```{r}

#png("MCMC_trace_hierarchical_model_2.png", width = 2000, height = 1500, res = 300)
mcmc_plot(hierarchical_model_2, type = "trace")
#dev.off()

#png("MCMC_dens_hierarchical_model_2.png", width = 2000, height = 1500, res = 300)
mcmc_plot(hierarchical_model_2, type = "dens")
#dev.off()
```



```{r}
#png("pp_check_density_hierarchical_model_2.png", width = 2000, height = 1500, res = 300)
pp_check(hierarchical_model_2, ndraws = 100)
#dev.off()


#png("pp_check_bar_hierarchical_model_2.png", width = 2000, height = 1500, res = 300)
pp_check(hierarchical_model_2, type = "bars")
#dev.off()
```



```{r}

#  LOO on Hierarchical Model 2

loo_hierarchical_model_2 <- loo(hierarchical_model_2)
print(loo_hierarchical_model_2)

png("loo_hierarchical_model_2.png", width = 2000, height = 1500, res = 300)
plot(loo_hierarchical_model_2)

```





##############  MODEL COMPARISON  ##################
####################################################
####################################################


```{r}
## Loo Comparison

# Compare the models
loo_comparison <- loo_compare(loo_ordinal_fit1, loo_ordinal_fit2,loo_hierarchical_model)
print(loo_comparison)# Print the comparison

```



<!-- ```{r} -->

<!-- # Compare the models -->
<!-- loo_comparison <- loo_compare(loo_ordinal_fit1, loo_ordinal_fit2,loo_hierarchical_model_2) -->
<!-- print(loo_comparison)# Print the comparison -->

<!-- ``` -->






####################### Prior Sensitivity Analysis #############################
################################################################################
################################################################################




# Prior Sensitivity Analysis For Ordinal_Model_Fit2 (Interaction term) (Model 2)


# Modifying ordinal_model_fit2 with different priors normal(0,1) and normal(0,10)

# Model with normal(0,1)

<!-- ```{r} -->

<!-- prior_sensitive_1 <- c( -->
<!--   set_prior("normal(0, 1)", class = "b"), -->
<!--   set_prior("normal(0, 1)", class = "Intercept") -->
<!-- ) -->

<!-- ordinal_model_fit2_normal_1 <- brm( -->
<!--   formula = Rating ~ International.Shipping * Product.Category, -->
<!--   data = merch_data_updated, -->
<!--   family = cumulative(), -->
<!--   prior = prior_sensitive_1, -->
<!--   sample_prior = TRUE, -->
<!--   iter = 2000, -->
<!--   warmup = 1000, -->
<!--   chains = 4, -->
<!--   cores = parallel::detectCores(), -->
<!--   seed = 123 -->
<!-- ) -->

<!-- ``` -->

<!-- ```{r} -->

<!-- saveRDS(ordinal_model_fit2_normal_1, file = "ordinal_model_fit2_normal_1.rds") -->

<!-- ``` -->


```{r}
ordinal_model_fit2_normal_1 <- readRDS("ordinal_model_fit2_normal_1.rds")
```


```{r}
summary(ordinal_model_fit2_normal_1)
```

# Model with normal(0,10)

<!-- ```{r} -->

<!-- prior_sensitive_2 <- c( -->
<!--   set_prior("normal(0, 10)", class = "b"), -->
<!--   set_prior("normal(0, 10)", class = "Intercept") -->
<!-- ) -->

<!-- ordinal_model_fit2_normal_10 <- brm( -->
<!--   formula = Rating ~ International.Shipping * Product.Category, -->
<!--   data = merch_data_updated, -->
<!--   family = cumulative(), -->
<!--   prior = prior_sensitive_2, -->
<!--   sample_prior = TRUE, -->
<!--   iter = 2000,  -->
<!--   warmup = 1000, -->
<!--   chains = 4,  -->
<!--   cores = parallel::detectCores(),  -->
<!--   seed = 123 -->
<!-- ) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- saveRDS(ordinal_model_fit2_normal_10, file = "ordinal_model_fit2_normal_10.rds") -->
<!-- ``` -->


```{r}
ordinal_model_fit2_normal_10 <- readRDS("ordinal_model_fit2_normal_10.rds")
```


```{r}
summary(ordinal_model_fit2_normal_10)
```

```{r}
summary(ordinal_model_fit2)
```


# Compare Posterior Distribution between 3 models


```{r}

plot(ordinal_model_fit2, type = "dens") 
plot(ordinal_model_fit2_normal_1, type = "dens")
plot(ordinal_model_fit2_normal_10, type = "dens")

```
```{r}

#png("ordinal_model_fit2.png", width = 2000, height = 1500, res = 300)
mcmc_plot(ordinal_model_fit2, type = "trace") 

```


```{r}

#png("ordinal_model_fit2_normal_1.png", width = 2000, height = 1500, res = 300)
mcmc_plot(ordinal_model_fit2_normal_1, type = "trace")

```

```{r}

#png("ordinal_model_fit2_normal_10.png", width = 2000, height = 1500, res = 300)
mcmc_plot(ordinal_model_fit2_normal_10, type = "trace")

```

# Visualize Differences in Posteriors

```{r}
variables(ordinal_model_fit2)

```

```{r}

# Density plots to visualize differences
mcmc_areas(
  as.array(ordinal_model_fit2),
  pars = c("b_International.ShippingNo", "b_Product.Category2",                     "b_Product.Category3","b_International.ShippingNo:Product.Category2","b_International.ShippingNo:Product.Category3")
  
)

```


```{r}

mcmc_areas(
  as.array(ordinal_model_fit2_normal_1),
  pars = c("b_International.ShippingNo", "b_Product.Category2",                     "b_Product.Category3","b_International.ShippingNo:Product.Category2","b_International.ShippingNo:Product.Category3")
  
  
)

```




```{r}

mcmc_areas(
  as.array(ordinal_model_fit2_normal_10),
  pars = c("b_International.ShippingNo", "b_Product.Category2",                     "b_Product.Category3","b_International.ShippingNo:Product.Category2","b_International.ShippingNo:Product.Category3")
  
)

```



# Prior Predictive Check

# Prior Predictive Check for ordinal_model_fit2 normal(0,5)

<!-- ```{r} -->


<!--   prior_sensitive_0 <- c( -->
<!--   set_prior("normal(0, 5)", class = "b"), -->
<!--   set_prior("normal(0, 5)", class = "Intercept") -->
<!-- ) -->

<!-- # Fit the model using only priors (Normal(0,5)) -->
<!-- ordinal_model_fit2_sens0 <- brm( -->
<!--   formula = Rating ~ International.Shipping * Product.Category,   -->
<!--   data = merch_data_updated,   -->
<!--   family = cumulative(),   -->
<!--   prior = prior_sensitive_0,  -->
<!--   sample_prior = "only",  # Generate data from prior samples only -->
<!--   iter = 2000,  -->
<!--   chains = 4, -->
<!--   control = list(adapt_delta = 0.999, max_treedepth = 20), -->
<!--   cores = parallel::detectCores(),  -->
<!--   seed = 123 -->
<!-- ) -->

<!-- ``` -->


<!-- ```{r} -->
<!-- saveRDS(ordinal_model_fit2_sens0, file = "ordinal_model_fit2_sens0.rds") -->
<!-- ``` -->



```{r}

ordinal_model_fit2_sens0 <- readRDS("ordinal_model_fit2_sens0.rds")

```


```{r}

# Prior predictive checks
pp_check(ordinal_model_fit2_sens0, ndraws = 100)

```





# Model with normal(0,1)

<!-- ```{r} -->


<!-- prior_sensitive_1 <- c( -->
<!--   set_prior("normal(0, 1)", class = "b"), -->
<!--   set_prior("normal(0, 1)", class = "Intercept") -->
<!-- ) -->

<!-- # Fit the model using only priors (Normal(0,1)) -->

<!-- ordinal_model_prior_sens1 <- brm( -->
<!--   formula = Rating ~ International.Shipping * Product.Category,   -->
<!--   data = merch_data_updated,   -->
<!--   family = cumulative(),   -->
<!--   prior = prior_sensitive_1,  -->
<!--   sample_prior = "only",  # Generate data from prior samples only -->
<!--   iter = 2000,  -->
<!--   chains = 4, -->
<!--   control = list(adapt_delta = 0.999, max_treedepth = 20), -->
<!--   cores = parallel::detectCores(),  -->
<!--   seed = 123 -->
<!-- ) -->



<!-- ``` -->


<!-- ```{r} -->
<!-- saveRDS(ordinal_model_prior_sens1, file = "ordinal_model_prior_sens1.rds") -->
<!-- ``` -->




```{r}

ordinal_model_prior_sens1 <- readRDS("ordinal_model_prior_sens1.rds")

```



```{r}
# Prior predictive checks
pp_check(ordinal_model_prior_sens1, ndraws = 100) 
```




# model with normal(0,10)

<!-- ```{r} -->


<!-- prior_sensitive_2 <- c( -->
<!--   set_prior("normal(0, 10)", class = "b"), -->
<!--   set_prior("normal(0, 10)", class = "Intercept") -->
<!-- ) -->

<!-- ordinal_model_prior_sens10 <- brm( -->
<!--   formula = Rating ~ International.Shipping * Product.Category, -->
<!--   data = merch_data_updated, -->
<!--   family = cumulative(), -->
<!--   prior = prior_sensitive_2, -->
<!--   sample_prior = "only", #Generate data from prior samples only -->
<!--   iter = 2000,  -->
<!--   control = list(adapt_delta = 0.999, max_treedepth = 20), -->
<!--   chains = 4,  -->
<!--   cores = parallel::detectCores(),  -->
<!--   seed = 123 -->
<!-- ) -->


<!-- ``` -->


<!-- ```{r} -->
<!-- saveRDS(ordinal_model_prior_sens10, file = "ordinal_model_prior_sens10.rds") -->
<!-- ``` -->


```{r}

ordinal_model_prior_sens10 <- readRDS("ordinal_model_prior_sens10.rds")

```


```{r}
# Prior Predictive Check
pp_check(ordinal_model_prior_sens10, ndraws = 100) 

```


# Prior Predictive vs Posterior Predictive

```{r}
#png("Normal0_5.png", width = 2000, height = 1500, res = 300)

library(gridExtra)

prior_plot <- pp_check(ordinal_model_fit2_sens0, ndraws = 100) +
  ggtitle("Prior Predictive Check")

posterior_plot <- pp_check(ordinal_model_fit2, ndraws = 100) +
  ggtitle("Posterior Predictive Check")

# Side-by-side arrangement
grid.arrange(prior_plot, posterior_plot, ncol = 2)

```




```{r}
#png("Normal0_1.png", width = 2000, height = 1500, res = 300)

library(gridExtra)

prior_plot <- pp_check(ordinal_model_prior_sens1, ndraws = 100) +
  ggtitle("Prior Predictive Check")

posterior_plot <- pp_check(ordinal_model_fit2_normal_1, ndraws = 100) +
  ggtitle("Posterior Predictive Check")

# Side-by-side arrangement
grid.arrange(prior_plot, posterior_plot, ncol = 2)

```




```{r}
#png("Normal0_10.png", width = 2000, height = 1500, res = 300)

library(gridExtra)

prior_plot <- pp_check(ordinal_model_prior_sens10, ndraws = 100) +
  ggtitle("Prior Predictive Check")

posterior_plot <- pp_check(ordinal_model_fit2_normal_10, ndraws = 100) +
  ggtitle("Posterior Predictive Check")

# Side-by-side arrangement
grid.arrange(prior_plot, posterior_plot, ncol = 2)

```





# Posterior Distributions Across Different Priors

```{r}


# Extracting posterior samples and add labels

# Posterior predictive check

#png("psteriordistribution 1.png", width = 2000, height = 1500, res = 300)

post_norm5 <- as_draws_df(ordinal_model_fit2) %>% mutate(Prior = "Normal(0,5)")
post_norm1 <- as_draws_df(ordinal_model_fit2_normal_1) %>% mutate(Prior = "Normal(0,1)")
post_norm10 <- as_draws_df(ordinal_model_fit2_normal_10) %>% mutate(Prior = "Normal(0,10)")

# Combining posterior samples into one dataframe

combined_post <- bind_rows(post_norm5,post_norm1, post_norm10)

# Reshaping data for plotting
combined_long <- pivot_longer(combined_post,
                              cols = starts_with("b_"),
                              names_to = "Parameter",
                              values_to = "Value")

# Generate the prior sensitivity comparison plot
ggplot(combined_long, aes(x = Value, color = Prior)) +
  geom_density(linewidth = 0.8, alpha = 0.8) +
  facet_wrap(~ Parameter, scales = "free") +
  theme_bw() +
  labs(title = "Posterior Distributions Across Different Priors",
       x = "Posterior Value",
       y = "Density",
       color = "Prior Distribution")
#dev.off()

```


# Check Model Fit using LOO-Comparison

```{r}
loo_ordinal_fit2 <- loo(ordinal_model_fit2)
loo_ordinal_fit2_normal_1 <- loo(ordinal_model_fit2_normal_1)
loo_ordinal_fit2_normal_10 <- loo(ordinal_model_fit2_normal_10)

print(loo_ordinal_fit2)
print(loo_ordinal_fit2_normal_1 )
print(loo_ordinal_fit2_normal_10)

```



```{r}
# Compare models
loo_comparison <- loo_compare(loo_ordinal_fit2,loo_ordinal_fit2_normal_1, loo_ordinal_fit2_normal_10)
print(loo_comparison)
```


```{r}

# Converting to dataframe for plotting

loo_df <- as.data.frame(loo_comparison)
loo_df$model <- rownames(loo_df)

# Plot Model Comparison

p <- ggplot(loo_df, aes(x = reorder(model, -elpd_diff), y = elpd_diff)) +
  geom_pointrange(aes(ymin = elpd_diff - se_diff, ymax = elpd_diff + se_diff),
                  size = 1, color = "red") +
  coord_flip() +
  labs(title = "Model Accuracy Comparison using LOO",
       x = "Model",
       y = "ELPD Difference (LOO)") +
  theme_minimal(base_size = 15) +
  theme(
    panel.background = element_rect(fill = "white"),
    plot.background = element_rect(fill = "white")
  )

# Display and save the plot

print(p)
ggsave("loo_comparison_plot.png", plot = p, width = 10, height = 6, dpi = 300)

```




<!-- ```{r} -->

<!-- Model Names -->

<!-- ordinal_model_fit1, ordinal_model_fit2 , ordinal_model_fit2_normal_1 , ordinal_model_fit2_normal_10,  -->

<!-- hierarchical_model,hierarchical_model_2 -->

<!-- prior predictive check : ordinal_model_fit2_sens0 , ordinal_model_fit2_sens1 , ordinal_model_fit2_sens10 -->

<!-- ``` -->


